%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.3in]{geometry} % Document margins
% \usepackage[utf8]{inputenc}
% \usepackage{cmtt}
\usepackage{xcolor}

\name{Shameel Arafin} % Your name
\address{469A Lexington Avenue, Apt 1 \\ Brooklyn, NY 11221} % Your address
\address{(215)~$\cdot$~982~$\cdot$~0854 \\ algebraist@gmail.com} % Your phone number and email

\begin{document}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Meredith Corp/former Time Inc}{April 2017 - February 2018}{Senior Director, Platform Engineering, News Group}{New York, NY}
\item Expanded purview to include Health vertical and all Foundry brands (auto, lifestyle) as well as branded/native efforts. Multimillion-dollar engagements with new and return clients, working closely with advertising and marketing teams.
\item Successfully launched multiple award-winning projects, including TIME's Person of the Year "The Silence Breakers" and "Finding Home", winner of ASME and POY awards.
\item Recruited and led more than a dozen developers, shaping a team whose composition approached gender parity (43\% female).
\item Deeply involved in mentoring throughout the company, in Product, Design and Engineering. 
\item Led engineering efforts for News and Health brands' second redesign, and re-platforming to Element (proprietary front-end platform).
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Time Inc}{August 2015 - April 2017}{Director, Platform Engineering, News Group}{New York, NY}
\item Led engineering team for News vertical, responsible for all technology aspects of time.com, fortune.com, money.com, timeforkids.com. Successfully launched iconic franchises such as FORTUNE 500, Person of the Year, TIME 100 Most Influential People.
\item Led redesign and re-platforming efforts for all News brands.
\item Led engineering for native/branded content engagements for The Foundry, the internal ad agency. Clients included Netflix and Siemens (seven-figure engagement).
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{MediaStorm}{June 2011 - July 2015}{Platform Architect \& Lead Developer}{Brooklyn, NY}
\item Responsible for architecture and back-end development of the MediaStorm Platform, an interactive storytelling platform. First online video player to implement transaction (pay to view), built on proprietary CMS. Key users/clients include Wall Street Journal's Infinity Awards, Sundance Institute, International Center for Transitional Justice. 
\item Led technology sections for MediaStorm Workshops
\item Recruited developers, initiated startup's 401(k) plan.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Various Startups \& Freelance Engagements}{January 2003 - June 2011}{CTO, Lead Developer}{New York, NY}
\item PopStay: Architected and coded the first prototype of social app for vacation rentals and home swapping.
\item Co-founded SignalFive, an interactive design, development and strategy agency for web/mobile apps. Clients included Al Gore's Alliance for Climate Protection, Grand Marnier. 
\item Massify: Back-end developer on social network/crowd-sourcing web application for the film and TV industry.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Credit Suisse First Boston Technology Group}{July 1998 - March 2002}{Senior Research Associate}{New York, NY}
\item Equity Research in Semiconductor Capital Equipment, Communications Test \& Measurement sectors. Deeply involved in Hewlett-Packard's divestiture of Agilent, largest tech IPO at the time.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Deutsche Bank Securities Technology Group}{June 1997 - July 1998}{Research Assistant}{New York, NY}
\item Equity Research in PC Hardware \& Software sectors for institutional investors, internal sales, trading, corporate finance and M\&A teams. Editor of \textit{The Tech Daily} and conference publications.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Harvard University, Cambridge, MA} \hfill {\em September 1995 - June 1997} \\ 
A.B. Literature (Honors)

{\bf California Institute of Technology, Pasadena, CA} \hfill {\em September 1993 - June 1995} \\ 
Electrical Engineering / Literature candidate\\

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
