%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.3in]{geometry} % Document margins
% \usepackage[utf8]{inputenc}
% \usepackage{cmtt}
\usepackage{xcolor}
\usepackage{hyperref}

\name{Shameel Arafin} % Your name
\address{469A Lexington Avenue, Apt 1 \\ Brooklyn, NY 11221} % Your address
\address{(215)~$\cdot$~982~$\cdot$~0854 \\ shameel@arafin.net \\ \href{https://www.linkedin.com/in/shameelarafin/}{https://www.linkedin.com/in/shameelarafin/}} % Your phone number and email

\begin{document}
%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}

Technology executive with extensive domain expertise in media, focused on digital journalism, documentary and online learning. Leader, mentor, engineering gender-parity advocate. 10+ years in web development, product management and project development.

\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Meredith Corp./formerly Time Inc.}{April 2017 - February 2018}{Senior Director, Platform Engineering, News Group}{New York, NY}
\item Successfully launched multiple award-winning projects, including  \href{http://time.com/time-person-of-the-year-2017-silence-breakers/}{TIME's Person of the Year ``The Silence Breakers"} and \href{http://time.com/finding-home/}{``Finding Home"}, winner of ASME and POY awards.
\item Led News and Health brands' second redesign and and \href{https://medium.com/@acharalambides/element-the-digital-unification-of-time-inc-979656149fd3}{re-platforming to Element} (proprietary front-end platform).
\item Recruited and led over a dozen developers, shaping a team whose composition approached gender parity (43\% female).
\item Expanded purview to include \href{http://www.health.com}{Health} vertical and all Foundry brands (\href{http://thedrive.com}{auto}, lifestyle) for the company's internal ad agency, as well as branded/native efforts. Managed multimillion-dollar engagements, working closely with advertising and marketing teams.
\item Deeply involved in mentoring throughout the company, in Product, Design and Engineering. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Time Inc.}{August 2015 - April 2017}{Director, Platform Engineering, News Group}{New York, NY}
\item Led engineering team for News and Education verticals, responsible for all technological aspects of \href{http://time.com}{time.com}, \href{http://fortune.com}{fortune.com},  \href{http://money.com}{money.com}, \href{https://www.timeforkids.com}{timeforkids.com}. 
\item Successfully re-launched iconic franchises such as \href{http://fortune.com/fortune500}{FORTUNE 500}, \href{http://time.com/time-person-of-the-year-2017-silence-breakers/}{Person of the Year}, \href{http://time.com/collection/most-influential-people-2018/}{TIME 100 Most Influential People}.
\item Led rearchitecture, re-platforming and development of \href{https://www.timeforkids}{Time For Kids}, from simple Drupal-based CMS to sophisticated WordPress VIP-powered learning management system including multiple lexile levels, Spanish translations, audio read-aloud of text, and online-assessment and testing software. 
\item Managed redesign and re-platforming efforts for all News brands to headless WordPress VIP.
\item Supervised engineering team for native/branded content engagements for The Foundry, for clients \href{http://time.com/paid-content-from/netflix/dinnertime/}{Netflix} and \href{http://time.com/partner/siemens/innovation-starts-here/}{Siemens} (seven-figure engagement).
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{MediaStorm}{June 2011 - July 2015}{Platform Architect \& Lead Developer}{Brooklyn, NY}
\item Created architecture and back-end development for MediaStorm Platform, an interactive storytelling tool. 
\item First online video player to \href{http://time.com/46716/game-changer-mediastorm-launches-pay-per-story-video-player/}{implement transaction (pay to view)}, built on proprietary CMS. Key users/clients include \href{https://mediastorm.com/clients/2018-icp-infinity-awards}{Wall Street Journal's Infinity Awards}, \href{https://mediastorm.com/clients/sundance-short-film-challenge}{Sundance Institute}, \href{https://mediastorm.com/clients/i-am-not-who-they-think-i-am-for-ictj}{International Center for Transitional Justice}. 
\item Led technology sections for MediaStorm Workshops
% \item Recruited developers, initiated startup's 401(k) plan.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Freelance Engagements}{January 2003 - June 2011}{CTO, Lead Developer}{New York, NY}
\item PopStay: Architected and coded the first prototype of social app for vacation rentals and home swapping.
\item Co-founded SignalFive, an interactive design, development and strategy agency for web/mobile apps. Clients included Al Gore's Alliance for Climate Protection, Grand Marnier. 
\item Massify: Back-end developer on social network/crowd-sourcing web application for the film and TV industry.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Harvard University, Cambridge, MA} \hfill {\em September 1995 - June 1997} \\ 
A.B. Literature (Honors)

{\bf California Institute of Technology, Pasadena, CA} \hfill {\em September 1993 - June 1995} \\ 
Electrical Engineering / Literature candidate\\

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
